Evaluación de impacto de la Reforma en Telecomunicaciones del 2013 en logro educativo en México

### 2021-05-11 final/pptx/presentacion.Rmd
update

.pull-left[
```{r, message= F, warning = F} 
out3<-rdplot(data$cambio_esp_top,data$cambio_internet,nbins=c(20,20),x.lim=c(-10,40),title="",x.label="Cambio Internet",y.label="Cambio Espanol", kernel = "triangular",c=9,h=4.572 ,p=1 , binselect = "qspr")
```
]

.pull-right[
```{r, message= F, warning = F} 
out4<-rdplot(data$cambio_mat_top,data$cambio_internet,nbins=c(20,20),x.lim=c(-10,40),title="",x.label="Cambio Internet",y.label="Cambio Espanol", kernel = "triangular",c=9,h=4.183 ,p=1 , binselect = "qspr")
```
]

>>>>

.pull-left[
```{r, message= F, warning = F,results='hide'} 
out3<-rdplot(data$cambio_esp_top,data$cambio_internet,nbins=c(20,20),x.lim=c(-10,40),title="",x.label="Cambio Internet",y.label="Cambio Espanol", kernel = "triangular",c=9,h=4.572 ,p=1 , binselect = "qspr")
```
]

.pull-right[
```{r, message= F, warning = F,results='hide'} 
out4<-rdplot(data$cambio_mat_top,data$cambio_internet,nbins=c(20,20),x.lim=c(-10,40),title="",x.label="Cambio Internet",y.label="Cambio Espanol", kernel = "triangular",c=9,h=4.183 ,p=1 , binselect = "qspr")
```
]
